---
title: "161122 Assignment C"
date: "Semester 2, 2023"
author: "Enter your name here"
output: 
  html_document:
    number_sections: yes
    code_download: true
    df_print: paged 
---

### About this assignment {-}

This assignment covers the material in topic C, including linear models with continuous and/or categorical predictors. If you have completed all the workshops in topic C, you should have seen most of the code you'll need to complete the assignment.

The assignment is assessed and should be your own work. You're welcome to discuss with other students, but submitted work must be your own.

### Instructions {-}

1. Download the .Rmd file by clicking the 'code' button on the top-right of this page.

2. Change the name of the .Rmd file to something like `Surname_StudentID_assignmentC.Rmd`. 

3. Open the file in RStudio. Each question is headed by '`##`'. Insert your code and written answers between the dashed lines below each question, like so.

     ````md
     ##

     The question is: Make a scatterplot of 1 to 5 vs 6 to 10. How does this make you feel?


     ::: {#answer style="color: #297EB1;"}

     ---------
     
     <!-- <answer here> -->

     ```{r}`r ''`
     plot(1:5,6:10)
     ```
     
     This makes me feel slightly patronised, and I'm now questioning my life choices.

     ---------
     
     :::
     ````

4. When you are finished, knit your .Rmd file to HTML and submit the .html file to the Assignment C dropbox on stream.


### Notes on grading {-}

1. There are 100 marks in total; 50 marks per section; 10 for each question.

2. There are typically multiple ways to achieve a correct answer for each question. We don't mind how an answer is achieved. As long as there is a clear, logical method used, full marks will be given.

3. We will provide advice if there is a better, faster, or cleaner way to achieve the same thing.

4. There are gold stars available for excellent answers. These do not typically count for final grade, but may make you (and the marker!) feel good.

5. We expect all charts to be appropriately labelled (axes with units if appropriate) and legible to achieve full marks.

6. We don't require charts to be pretty, beyond being correctly labelled and legible. Students are welcome to make them pretty though!

### Set up {-}

```{r setup general, message=FALSE, class.source="bg-success"}
# Don't change this chunk unless you know what you're doing :)
# Make sure you've installed each of these packages.
library(tidyverse)
library(visreg)
library(tsibble)
library(lubridate)
library(broom)
# The stuff below changes some aesthetic options for the output
knitr::opts_chunk$set(message = FALSE) # omit messages from r
knitr::opts_chunk$set(out.width="70%", fig.width=6, fig.height=4, fig.retina=2) # size graphs
knitr::opts_chunk$set(class.source="bg-info", class.output="bg-warning") # colour of code boxes
theme_set(theme_bw())
```

Do not alter the chunk below. It puts a box around your answers and turns the text blue, which will help with marking.

```{css, echo=TRUE}
#answer {
  color: #297EB1;
  border: 1px solid #000;
  padding: 10px;
}
```


##### And now... the questions. {-}


---------


# Rubbery spider silk

The first section is based on a study of the 'rubberiness' of spider silk. Rubber has a property called 'negative thermal expansion', meaning that it increases in elasticity (gets tighter) under higher temperatures.

Load the file `webs.csv` into R.


```{r data1, class.source="bg-success", class.output=""}
webs <- read_csv(file="https://www.massey.ac.nz/~jcmarsha/161122/data/webs.csv")
glimpse(webs)
```
There are three columns:

`obs` is an observation number     
`length` is the relative length of the silk after exposure to temperature     
`temp.C` is the temperature to which the silk was exposed.

The research question is: does the relative length decrease with temperature?


##  

Make a ggplot of `length ~ temp.C` and add a 'smooth' line to it. Comment on the pattern. Is there a relationship? Is it linear?

::: {#answer}

<!-- <answer here> -->

```{r 1.1}

```

:::


##

Fit a simple linear regression model. Summarise the model, and visualise the model on a plot of the data. Comment on the fit of the model. In particular, is the relationship statistically significant? What proportion of the variation in $y$ is explained by the model?

::: {#answer}

<!-- <answer here> -->

```{r 1.2}

```

:::



## 

Make the four standard diagnostic plots. Do you see any evidence that any assumptions of linear regression are violated? Are there any problematic outliers?

::: {#answer}

<!-- <answer here> -->

```{r 1.3}

```

:::



## 

a) In the following equation, replace the values $a$ and $b$ with the appropriate estimates from your model. *Hint: use the `tidy()` function on your model to get a nicer summary.*

$$
\text{mean}[length] = a + b \times temp.C
$$

b) Now use the `augment` function (or other) to predict the mean length at a temperature of 30 degrees. Provide 95% confidence *and* prediction intervals for your prediction. Which interval is wider, and why?

::: {#answer}

<!-- <answer here> -->

```{r 1.4}

```

:::


## 

Fit an alternative model of `length`, this time as a quadratic function of `temp.C`. A good way to do this is using the `poly` function 

*Hint: the formula `length ~ poly(temp.C, 2)` fits a polynomial of order 2; that is, `y ~ x + x^2`.*

a) Make a summary of the quadratic model. Compare it to the linear model. Which of these would you use to make predictions of silk length based on temperature, and why?

b) Make a plot of the data, with `temp.C` on the x-axis and `length` on the y-axis. Add a line of the predicted mean `length` based on the quadratic model. How does it differ, qualitatively, from the first model?

::: {#answer}

<!-- <answer here> -->

```{r 1.5a}

```


```{r 1.5b}

```

:::




# New Zealand incomes

```{r setup2, class.source="bg-success"}
# Don't change this chunk unless you know what you're doing :)
nzincome <- 
  read_csv(file="https://www.massey.ac.nz/~jcmarsha/161122/data/NZIncomes11.csv") |>  
  mutate(sex = factor(sex)) |> 
  mutate(ethnicity = factor(ethnicity)) 

nzincome
```

## 

Produce plots of the weekly income (`income`) versus the variables `ethnicity`, `sex`, `agegrp`,`qualification` and `hours`, ensuring you clearly label axes. Comment on the plots, particularly with respect to whether there is (graphical) evidence for an association with the weekly wages.


::: {#answer}

<!-- <answer here> -->

```{r 2.1}

```

:::


## 

Fit a model of log weekly income (`income`) as a linear function of the variables `ethnicity`, `sex`, `agegrp`,`qualification` and `hours`.  Peruse the R summary and interpret each significant coefficient at the level 0.05.


::: {#answer}

<!-- <answer here> -->

```{r 2.2}

```

:::

## 

Produce model diagnostic plots. Are the assumptions of the linear model met? Explain your reasoning.

::: {#answer}

<!-- <answer here> -->

```{r 2.3}

```

:::


## 

Produce a prediction for the weekly income of a 25 years old Asian man with a bachelors degree (qualification level 4) working 40 hours per week along with a 95% prediction interval. Interpret this interval in words that a client may understand.

::: {#answer}

<!-- <answer here> -->

```{r 2.4}

```

:::


## 

Refit a multivariable linear model for log weekly income by adding an interaction term between `ethnicity` and `qualification`. Peruse the R summary and discuss your findings.

::: {#answer}

<!-- <answer here> -->

```{r 2.5}

```

:::
